Methodology for Assessing the State of the Practice for Domain X

### 2020-09-19 StateOfPractice/Methodology/Methodology.tex
copied over Olu's Research Questions into Methodology doc Section 2, made some adjustment, added comments - Section is still WOP

\section{Research Questions}\label{ResearchQuestions}

In general questions:

\begin{enumerate}
\item Comparison between domains
\item How to measure qualities
\item How does the quality compare for projects with the most resources to those
  with the fewest?
\item What skills/knowledge are needed by future developers?
\item How can the development process be improved?
\item What are the common pain points?
\end{enumerate}

For each domain questions''

\begin{enumerate}
\item Best examples within the domain
\item What software artifacts?
\item What are the pain points?
\item Any advice on what can be done about the pain points?
\end{enumerate}

Measure the effort invested and the reward.  Related to sustainability.

Collect the data and see what conclusions follow.  For an individual domain,
between domains.  The process isn't so much about ranking the software as it is
about looking at the software closely and see what conclusions arise.  The
measurements are intended to force scrutiny, from different perspectives.

>>>>

\section{Research Questions}\label{ResearchQuestions}
	\begin{enumerate} 
		\item What artifacts are recommended for research software development?
\pmi{remove}
		\item What artifacts do current software projects produce?
\pmi{keep}
		\item What artifacts are produced in existing software development processes. 
\pmi{remove}
		\item What information is captured by current projects artifacts?
\pmi{keep}
		\item What information is necessary to capture for sustainability and productivity?
\pmi{need to review - subjective, can we capture this from gathering state of practice data?}
		\item What commonalities exist among software artifacts?
\pmi{keep}
		\item What are sustainable and productive methods to produce softifacts?
\pmi{remove}
		\item What are the consequences of technology tools towards sustainability and productivity  \pmi{keep, reword: what technology tools are used? what do they capture? benefits?}
		\item What are the common factors that lead to sustainability and productivity?
\pmi{need to review, reword. How do we gather sustainability from SOP data?}
		\item What relationships exist, if any, between 'high ranking' software projects and sustainability/productivity?
 \pmi{need to review}	
		\item What skills/knowledge are needed by future developers?	\pmi{copied from original - review}
		\item What are the common pain points?	\pmi{copied from original - review}
		\item How can the development process be improved?	\pmi{copied from original - review}
	\end{enumerate}

%In general questions:
%
%\begin{enumerate}
%\item Comparison between domains
%\item How to measure qualities
%\item How does the quality compare for projects with the most resources to %those
%  with the fewest?
%\item What skills/knowledge are needed by future developers?
%\item How can the development process be improved?
%\item What are the common pain points?
%\end{enumerate}
%
%For each domain questions''
%
%\begin{enumerate}
%\item Best examples within the domain
%\item What software artifacts?
%\item What are the pain points?
%\item Any advice on what can be done about the pain points?
%\end{enumerate}
%
%Measure the effort invested and the reward.  Related to sustainability.
%
%Collect the data and see what conclusions follow.  For an individual domain,
%between domains.  The process isn't so much about ranking the software as it is
%about looking at the software closely and see what conclusions arise.  The
%measurements are intended to force scrutiny, from different perspectives.
